Textmining in Economics

### 2017-10-14 textm.Rmd
new examples

- In economics, empirical work is largely based on quantitative data (e.g. prices, demand, votes, etc.)
- But a large amount of unstructured text is also generated in economic environments (e.g. company reports, court decisions, media articles, etc.)
- At an abstract level, text is simply a string of characters.
    - Latin alphabet ('a', 'A', 'p' and so on)
    - Punctuation (e.g. !), 
    - Numbers, 
    - Non-alphanumerical characters (e.g. @)

@@

@@

1. Represent the textual database $D$ (**document**) as a numerical array $\boldsymbol{C}$ (**corpus**)
  - *Text-preprocessing, Bag-of-words model*

>>>>

- In economics, empirical work is largely based on quantitative data (e.g. prices, demand, votes, etc.)
- But a large amount of unstructured text is also generated in economic environments (e.g. company reports, court decisions, media articles, etc.)
- At an abstract level, text is simply a string of characters 
    - Latin alphabet ('a', 'A', 'p' and so on), Punctuation (e.g. !), Numbers,Non-alphanumerical characters (e.g. @)

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(tweets, aes(date, fill = partei)) + 
    geom_histogram(alpha = .8, adjust = .25, binwidth = 500) +
    scale_fill_manual(name = "", values = c("deepskyblue1", "black","limegreen", "darkorchid2","gold", "red2")) +
    xlab("") +
    ylab("Anzahl der Tweets") +
    scale_x_datetime(breaks = date_breaks("2 hour"), labels=date_format("%a-%d\n%H:%M", tz="CET"))
```

@@

1. Pre-process the text (Stopword removal, tokenization, stemming) and Represent(**document** $D$ as a numerical array $\boldsymbol{C}$ (e.g. *bag-of-words model*)
